---
title: "SDS 315 HW 8"
subtitle: "https://github.com/sophiayang5/SDS-315-HW-8"
author: "Sophia Yang (sy23928)"
output:
  pdf_document:
    toc: true
    toc_depth: 5
    number_sections: false
date: "2025-04-09"
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(ggplot2)
library(tidyverse)
library(mosaic)
```

\newpage
# Problem 1: Regression Warm Up
```{r, include = FALSE}
creatinine <- read.csv("creatinine.csv")
```

## Part A)
```{r, include = FALSE}
# create the linear regression model
creatlm = lm(creatclear ~ age, data = creatinine)
coef(creatlm)
```
For a 55-year old, we expect the creatinine clearance rate to be 113.71. I determined this by finding the equation for the linear regression model, which is y = 147.81 - 0.62 * age, and plugging in 55 for age.

## Part B)
The creatinine clearance rate decreases at rate of 0.62 mL/minute/year. I determined this by finding the slope of the linear regression model for creatinine clearance rate predicted by age.

## Part C)
The 40-year-old's creatinine clearance rate is healthier for their age. I determined this by calculating the expected clearance rates for the 40-year-old and the 60-year-old with the linear regression equation (y = 147.81 - 0.62 * age): the 40-year-old's expected rate was 123.01, and the 60-year-old's expected rate was 110.61. Then, I took the difference between their actual rates and their expected rates: the 40-year-old's difference was 11.99, and the 60-year-old's was 1.39. Finally, I chose the person with the greater positive difference, which was the 40-year-old.

\newpage
# Problem 2: Modeling Disease Growth
```{r}
covid <- read.csv("covid.csv")
```

```{r, include = FALSE}
# filter for Italy
italy = filter(covid, country == "Italy")
# create the exponential model
italy_lm = lm(log(deaths) ~ days_since_first_death, data = italy)
coef(italy_lm)

# find the bootstrapped confints
boot_italy_lm = do(10000)*lm(log(deaths) ~ days_since_first_death, data = mosaic::resample(italy))
confint(boot_italy_lm, level = 0.95)


# filter for Spain
spain = filter(covid, country == "Spain")
# create the exponential model
spain_lm = lm(log(deaths) ~ days_since_first_death, data = spain)
coef(spain_lm)

# find the bootstrapped confints
boot_spain_lm = do(10000)*lm(log(deaths) ~ days_since_first_death, data = mosaic::resample(spain))
confint(boot_spain_lm, level = 0.95)
```
For Italy, the estimated growth rate is 0.183, with a bootstrapped 95% confidence interval of (0.159, 0.208), while the estimated doubling time is 3.8 days, with a 95% confidence interval of (3.4, 4.4).

For Spain, the estimated growth rate is 0.276, with a bootstrapped 95% confidence interval of (0.234, 0.318), while the estimated doubling time is 2.5 days, with a 95% confidence interval of (2.2, 3.0).

```{r}
# line graph showing reported daily deaths over time
ggplot(covid) + geom_line(aes(x = days_since_first_death, y = deaths, color = country)) +
  labs(
    title = "Relationship Between COVID Deaths and Time",
    x = "Days Since 1st Death",
    y = "Deaths",
    color = "Country:"
  )
```

\newpage
# Problem 3: Price Elasticity of Demand
```{r, include = FALSE}
milk <- read.csv("milk.csv")

# create the power law model
milk_lm = lm(log(sales) ~ log(price), data = milk)
coef(milk_lm)

# find the bootstrapped confint
boot_milk_lm = do(10000)*lm(log(sales) ~ log(price), data = mosaic::resample(milk))
confint(boot_milk_lm, level = 0.95)
```
The estimated price elasticity of demand for milk is -1.62, with a bootstrapped 95% confidence interval of (-1.77, -1.46). To estimate the elasticity, I created a linear regression model for the log of sales predicted by the log of prices; thus, the coefficient of -1.62 would be the estimated price elasticity. Additionally, I repeatedly resampled from the dataset and created those linear regression models for each sample to find the boostrapped 95% confidence interval of (-1.77, -1.46).
